Title here

### 2016-12-12 portfolio/text/ms.Rmd
Edit intro

Commercial fishers present an interesting example of diversification, given the
extreme risk that some individuals experience, particularly relative to
terrestrial agriculture [@sethi2012b]. The majority of risk insurance programs
available to terrestrial farmers (e.g. crop insurance programs) are not
obtainable by commercial fishers [@kasperski2013], possibly because both fish
and fishers are spatially mobile. However, fishers still have the ability to
lower risk. They can, for example, target as many species as permitted by
a license, own multiple licenses, or diversify spatially and fish in multiple
regions.

The effectiveness of these diversification strategies for increasing revenue and
reducing revenue variability remains uncertain. For example, theory and
empirical studies suggest there can be substantial benefits to specialization
for both farmers and fishers [@abdulai2000; @arnason2005]. Furthermore, the
majority of research examining the effects of diversification on revenue do so
at aggregate levels that combine individuals (e.g. households, counties, or
communities; [@kasperski2013; @sethi2014]). Because of this, key uncertainties
remain about the fundamental relationship between diversity, fishing revenue,
and fishing revenue variability at the level of the individual.

@@

Our model is a variance-function regression model [@davidian1987; @hall1989],
which simultaneously models changes in the mean and variance of individual
revenue as a function of covariates. Whereas traditional hierarchical linear
models assume homoscedasticity --- that the residual variance does not vary
systematically --- the variance-function regression model allows the variance to
be heteroscedastic and vary as a function of predictors. Our specific model
simultaneously estimates the effect of species diversity on individual revenue
and revenue variability, and estimates effects both within and across fishing
strategies (sets of similar licenses or permits). At the same time, it controls
for fishing effort and latent time effects (e.g. changing environmental
conditions). To our knowledge, this is the first application of this type of
model in any natural resource field.

>>>>

Commercial fishers present an interesting example of diversification, given the
extreme risk that some individuals experience, particularly relative to
terrestrial agriculture [@sethi2012b]. The majority of risk insurance programs
available to terrestrial farmers (e.g. crop insurance programs) are not
obtainable by commercial fishers [@kasperski2013], possibly because both fish
and fishers are spatially mobile. However, fishers still have the ability to
lower risk. They can, for example, target as many species as permitted by
a license, own multiple licenses, or diversify spatially and fish in multiple
regions. The effectiveness of these diversification strategies for increasing
revenue and reducing revenue variability remains uncertain. For example, theory
and empirical studies suggest there can be substantial benefits to
specialization for both farmers and fishers [@abdulai2000; @arnason2005].
Furthermore, the majority of research examining the effects of diversification
on revenue do so at aggregate levels that combine individuals (e.g. households,
counties, or communities; [@kasperski2013; @sethi2014]). Because of this, key
uncertainties remain about the fundamental relationship between diversity,
fishing revenue, and fishing revenue variability at the level of the individual.

@@

Our model is a variance-function regression model [@davidian1987; @hall1989],
which simultaneously models changes in the mean and variance of individual
revenue as a function of covariates. Whereas traditional hierarchical linear
models assume homoscedasticity --- that the residual variance does not vary
systematically --- the variance-function regression model allows the residual
variance to be heteroscedastic and vary as a function of predictors. Our
specific model simultaneously estimates the effect of species diversity (the
inverse of Simpson's diversity index [@simpson1949; @jost2006]) on individual
revenue and revenue variability, and estimates effects both within and across
fishing strategies (sets of similar licenses or permits). At the same time, it
controls for fishing effort and latent time effects (e.g. changing environmental
conditions). To our knowledge, this is the first application of this type of
model in any natural resource field.
